---
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_book:
    keep_tex: no
params:
  title: '[TITLE HERE]'
  author: '[AUTHOR HERE]'
  date: '[DATE HERE]'
  description: '[DESCRIPTION HERE]'
# To show all the references with no in-text citations, please uncomment this line of code.
#nocite: '@*'
# If you want some (not all) references with no in-text citations, please uncomment this line of code and modify.
#nocite: | 
#  @item1, @item2
---

```{r include=FALSE}
# Libraries to load here.
library(knitr)
library(ggplot2)
```

---
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center}\vspace{-1.3cm}\LARGE\includegraphics[width=5cm]{ONDRI_full-logo_web.png}\\[\bigskipamount]\hfill\break}
- \posttitle{\end{center}}
- \preauthor{\begin{center} \vspace{0.3cm}}
- \postauthor{\vspace{0.3cm} \end{center}}
- \predate{\begin{center}}
- \postdate{\\[\bigskipamount] \vspace{0.3cm} \hrulefill \end{center} \vspace{0.6cm} `r params$description`}
title: `r params$title`
author: `r params$author`
date: `r params$date`
documentclass: article
fontsize: 10pt
geometry: margin=2.54cm
---

```{r, include=FALSE}
# copy the R logo to the current directory
file.copy(file.path('C:/document_similarity_checker/www/ONDRI_full-logo_web.png'), '.')
```