---
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_book:
    keep_tex: no
params:
  title: 'Proposal Similarity Report'
  # author: '[AUTHOR HERE]'
  date: '[Date]'
  description: 'This report checks the similarity between previously approved proposals against newly submitted proposals.'
# To show all the references with no in-text citations, please uncomment this line of code.
#nocite: '@*'
# If you want some (not all) references with no in-text citations, please uncomment this line of code and modify.
#nocite: | 
#  @item1, @item2
---


```{r include=FALSE}
# Libraries to load here.
# library(knitr)
# library(kableExtra)

date <- Sys.Date()
```
---
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center}\vspace{-1.3cm}\LARGE\includegraphics[width=5cm]{ONDRI_full-logo_web.png}\\[\bigskipamount]\hfill\break}
- \posttitle{\end{center}}
- \preauthor{\begin{center} \vspace{0.3cm}}
- \postauthor{\vspace{0.3cm} \end{center}}
- \predate{\begin{center}}
- \postdate{\\[\bigskipamount] \vspace{0.3cm} \hrulefill \end{center} \vspace{0.6cm} `r params$description`}
title: `r params$title`
author: `r params$author`
date: `r date`
documentclass: article
fontsize: 10pt
geometry: margin=2.54cm
---

```{r, include=FALSE}
# copy the logo to the current directory
file.copy(report_path(), ".")
```

```{r, echo=FALSE}
data <- similar_articles_df()[order(-similar_articles_df()$common_words_weighted),]
```

```{r, results='asis', echo=FALSE}
for (i in 1:length(data$proposal_title)){
   cat('\n')  
   cat("Proposal Title:", data$proposal_title[i], "\n")
   cat('\n') 
   cat('\n')  
   cat("Author:", data$author_of_proposal_title[i], "\n")
   cat('\n') 
   cat("Similar Proposal Title:", data$most_similar_proposal_title[i], "\n")
   cat('\n') 
   cat('\n')
   cat("Number of Common Words:", length(unlist(data$common_words_list[i])), "\n")
   cat('\n')
   if (length(data$common_words_weighted[i]) == 0) {
      cat('\n')
      cat("Similarity Indicator:","NOT SIMILAR", "\n")
      cat('\n')
   }
     else if (data$common_words_weighted[i] >= 1 & data$common_words_weighted[i] < 6) {
       cat('\n')
       cat("Similarity Indicator:","NOT VERY SIMILAR", "\n")
       cat('\n')
   }
     else if (data$common_words_weighted[i] >= 6 & data$common_words_weighted[i] < 10) {
       cat('\n')
       cat("Similarity Indicator:","SOME SIMILARITY", "\n")
       cat('\n')
   } else if (data$common_words_weighted[i] >= 10) {
       cat('\n')
       cat("Similarity Indicator:","SIMILAR", "\n")
       cat('\n')
   }
   cat("Author of Similar Proposal:", data$author_of_most_similar_proposal[i], "\n")
   cat('\n') 
   cat('\n')
   cat("Common Words List:", paste(unlist(data$common_words_list[i]), collapse=', '), '\n')
   cat('\n') 
   cat("---------------------------------------------------", '\n')
}
```
